Technical Report

### 2018-02-14 fully-abstract-comp/technical-report.tex
Make the colors more readable.

\documentclass[a3paper]{article}
\usepackage[a3paper,margin=0.7in]{geometry}
\usepackage[utf8]{inputenc}

@@

\subsection{Future world}
\subsubsection{\color{green} first thoughts on change to future world relation}
{\color{green}
The public part of the future world relation stays the same:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \pubft W(r) }
            { W' \future W }
\end{mathpar}
The private future world relation becomes:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \privft W(r) \\  \exists r \in \dom(W') \setminus \dom(m(W))\ldotp W'(r) \text{ is non-empty and stack region}}
            { W' \future W }
\end{mathpar}
where we take "is non-empty and stack region" to mean the following:

@@

\subsection{Memory satisfaction}
{\color{green}
Memory satisfaction for new worlds:
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \stk = (\opc_0,\ms_0):: \dots :: (\opc_m,\ms_m) \wedge \\
      \ms_S \uplus \ms_\stk \uplus \ms_0 \uplus \dots \uplus \ms_m  \wedge\\
      \exists \ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}\ldotp \\
      \quad \ms_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus \ms_\var{T,heap} \wedge \\
      \quad \memSatStack{\stk,\ms_\var{T,stack}}{W} \wedge \\
      \quad \memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W} \wedge \\
      \quad \memSatHeap{\ms_S,\ms_\var{T,heap}}{W}
    \end{array}
  \right.
\]

>>>>

\documentclass[a3paper]{article}
\usepackage[svgnames]{xcolor}
\usepackage[a3paper,margin=0.7in]{geometry}
\usepackage[utf8]{inputenc}

@@

\subsection{Future world}
\subsubsection{\color{DarkGreen} first thoughts on change to future world relation}
{\color{DarkGreen}
The public part of the future world relation stays the same:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \pubft W(r) }
            { W' \future W }
\end{mathpar}
The private future world relation becomes:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \privft W(r) \\  \exists r \in \dom(W') \setminus \dom(m(W))\ldotp W'(r) \text{ is non-empty and stack region}}
            { W' \future W }
\end{mathpar}
where we take "is non-empty and stack region" to mean the following:

@@

\subsection{Memory satisfaction}
{\color{DarkGreen}
Memory satisfaction for new worlds:
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \stk = (\opc_0,\ms_0):: \dots :: (\opc_m,\ms_m) \wedge \\
      \ms_S \uplus \ms_\stk \uplus \ms_0 \uplus \dots \uplus \ms_m  \wedge\\
      \exists \ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}\ldotp \\
      \quad \ms_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus \ms_\var{T,heap} \wedge \\
      \quad \memSatStack{\stk,\ms_\var{T,stack}}{W} \wedge \\
      \quad \memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W} \wedge \\
      \quad \memSatHeap{\ms_S,\ms_\var{T,heap}}{W}
    \end{array}
  \right.
\]
